Learning Actionable Analytics (with applications for reducing defects and reducing runtimes)

### 2015-05-12 how.tex
Updates from ShareLaTeX

\usepackage{subfig}
\usepackage{wrapfig}
 \usepackage{amsmath}
 \usepackage{url}
 \usepackage{pifont}
 %\usepackage{times}
\usepackage{rotating}
%\usepackage{balance} 
\usepackage{color, colortbl}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage[running]{lineno}
\usepackage{program}
\usepackage{cite}
\usepackage{alltt}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\textsection\ref{sec:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\definecolor{lightgray}{gray}{0.975}
\usepackage{fancyvrb}
\usepackage{stfloats}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amsmath}  
\DeclareMathOperator*{\argmin}{arg\,min} 
\DeclareMathOperator*{\argmax}{arg\,max} 
%\usepackage[usenames]{xcolor}

@@

\title{Learning Actionable Analytics 
 (with applications for reducing defects and reducing runtimes)}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each Slope of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
Rahul Krishna, Tim Menzies, Xipeng Shen\\
        Computer Science, NcState, USA\\
       \{i.m.ralk, tim.menzies, xipengshen\}\@gmail.com
% 3rd. author
 % use '\and' if you need 'another row' of author names
% 4th. author
\and
 Andrian Marcus\\
       Computer Science, UtDallas, USA \\
       amarcus\@utdallas.edu }

@@

This is an open and pressing issue.
Business  users   now demand   data mining tools
that  support a  business-level
interpretation of that data. For example,
at a  panel on software analytics at ICSE'12,
industrial practitioners lamented the state of the art in data mining
and software engineering~\cite{menzies12a}. Panelists commented that
``prediction is all well and good, but what about decision
making?''. That is, these panelists are more interested in the interpretations
and follow-up
that occurs {\em after} the mining, rather than just  the mining itself; e.g.
\bi
\item 
Instead of just accepting  {\em predictions} on how many 
 software defects
to expect,  business users might now demand a {\em plan} to
reduce the likelihood of those defects;
\item Instead of just accepting {\em predictions} on the runtime
time of their software, business users might now demand
a {\em plan} to reduce that runtime.
\ei
How to assess such {\em plans}?
Some organizations have the resources to 
run repeated trials to assess  different treatments.
For example, in one remarkable recent study, Bente et al. report results
were the same specification was developed into a product by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
to (say) take a code base, assign it to $N$ different teams, apply
HOW's plans the code used by  $N/2$ teams, then check in 12 months time
if those halves of the teams have fewer defects than the other.

@@

The planner explored in this paper is the ``HOW'' case-based planner.
HOW's  ``plans'' are  set of changes
proposed  in order to better achieve some goal. 
Specifically, for every test case $Z$, HOW proposes a  plan $\delta$ to
  adjust   attributes $Z_j$:
\begin{equation}\label{eq:one}
Z_j = Z_j + \delta_j
\end{equation}
For example, to simplify a  large bug-prone  method, HOW might suggest
to a developer to reduce its size (i.e.  refactor that code by, say, splitting it across
two simpler functions).

@@

However, not all domains come with ready-to-use models.
For   several problems where models are hard to obtain, or the input and output are related by complex connections that simply cannot be modeled in a reliable manner~\cite{Ludewig2003}. For example, 
consider software defect prediction and all the intricate issues that may lead defects in a product. A odel that includes {\em all} those
potential issues would be very large and unweliding. Further,
the empirical data required to validate any/all parts
of that model can be hard to find.

In fact, our experience has been that accessing and/or commissioning
a model can be a labor-intensive process.
For  example, in previous work~\cite{me07f} we used models
developed by Boehm's group at the University of Southern California.
Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).

@@

\subsection{Planning and AI}
HOW is a {\em probablistic} planner, which is a different approach to that taken by
classical AI. 
That kind of planning is a logical procedure~\cite{Fikes1971}
that seeks an ordering on {\em operators} to take some domain
{\em state} from a {\em start} state to a {\em goal} state.
This classical logical approach is known to suffer from
computational bottlenecks~\cite{Bylander1994}. Hence,
like this paper,
many researchers take a probabilistic approach.
HOW's commitment to minimal displacement (and the fully-automated
modeling approach) of this paper makes it stand apart from, say,
  the Bayesian/Markov chain approach to planning of Dean et al.~\cite{dean1995planning}.

\subsection{Case-based Reasoning}
Case-based reasoning (CBR) has been extensively
explored in the AI literature
(where it has also bee called
 reasoning via anology or instance-based reasoning).
CBR seeks to emulate human recollection and adaptation
of past experiences in order to find solutions to current
problems.

@@

Secondly, the output of a CBR is made on a ``case-by-case'' basis. 
That is, CBR does not offer some trite generalization over multiple
exmaples. Rather, the advice it gives is specialized to the particular
case being considered at the current time.  This is particularly attractive
since much of our recent work has focused on issues
of locality (where the best solutions for some part of the data
are very different some average case solution obtained from all the data~\cite{localvsglobal}).

@@

Generation two of that work resulted in  IDEA~\cite{me12c}.
IDEA and HOW use the    same recursive clustering
method but IDEA made the mistake of  summarize those
recursive divisions into a tree structure. Initial results with IDEA were weak, but somewhat
positive~\cite{me12c}. We tried unsuccessfully for  months to extend and improve
the IDEA prototype. The results were most discouraging: those tree-based summaries often suffered
from the same optimization failure problem seen with W2.

@@

Turning now to the displacement {\em direction},
our experiments show that it useful to  carefully reflect on exactly where HOW should  push each test case.
HOW replaces each cluster   with one {\em exemplar} that best
characterizes the data in that cluster. It then displaces the
test data towards that exemplar, as shown in \fig{howcode}, line 20. In summary, 
If  $Z_j$ is an independent variable within the
test case $Z$ and  $X$ is the exemplar found at training time,
then we displace $Z_j$ as follows:
\[Z_j =  Z_j + F*(X_j - Z_j)\]
Here, $F$ is the  magnitude controller, discussed above.

Different kinds of data require
different policies for exemplar generation.
For the Jureczko data, the objective score
is a boolean variable is true if defects have been noted
for that class.  For this kind of data (with discrete objectives),
we found nothing better than  making the exemplar of a cluster be the mean
value of all attributes of all cases in that cluster.

However, for the Seigmund data, we found a better exemplar generation policy.
\fig{pp} shows the effects of selecting different kinds of exemplars for 
Berkeley DB, one of the Seigmund data sets.
The \textcolor{black}{\bf black baseline} curve  shows the runtimes for 600 random configurations
of the Makefiles used in Berkely DB. The other two curves shows the predictions of the runtimes if test cases are displaced towards exemplars
  built from:
\bi
\item The \textcolor{red}{\bf   mean}    value of all cases in the  cluster.
\item The  case with the \textcolor{green}{\bf  best}  objective score. 
\ei
Note that using the best as the exemplar does better than useing the mean.
The general pattern shown of \fig{pp} has been seen in all the Seigmund data sets;
i.e. for data sets with continuous classes,
best results come from using exemplars formed from the best instance (and not the mean).

@@

    \caption{Training and test {\em data set properties} for the Jureczko data sets,
    sorted in ascending order of \% defective examples.
    On the right-hand-side, we show the {\em results from learning}.
    Data is ``good'' if it has   recalls over 60\% and false alarms under 40\%
(and note that, after tuning, there are more ``good'' than before).
Data   marked with ``$\star$'' show large improvements in performance, after tuning.
Data   marked with ``$\times$'' are not ``good'' since their test suites  have so few undefective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
}\label{fig:j}
\end{figure*}

@@

As shown in \fig{work}, our proposal divides
project data  into two disjoint sets {\em train} and {\em test}
(so \mbox{{\em train} $\cup$ {\em test} $=\;\emptyset$}).
Next, from the train set, we build both a {\em planner} as well
as a {  predictor}. Our general framework does not   commit to any particular  choice
of { planner} or { predictor} but, for the purposes of this paper, 
our { planner}
will be HOW  and our
our { predictors} will be the Random Forest~\cite{Breiman2001} and Random Forest
Regressor taken from the SciKit
Learn toolkit~\cite{Pedregosa2012}.  
%\begin{figure}[t!]
%\small
%\begin{tabular}{|p{.95\linewidth}|}\hline
% Decision tree learners find the attribute whose value's
%select for for sections of the data with least variation in the class
%variable. Decision tree learners then recurse on each selection~\cite{breiman84}. 
%
%A random forest is a set of decision trees, each built
%from some random subset of the rows and columns. The conclusions
%of the forest are a ``vote'' generated by all the trees~\cite{Breiman2001}. 
%
%A standard Random Forest predicts for a discrete class variable while
%a Random Forest Regressor generates numeric predictions.\\\hline
%\end{tabular}
%\caption{Random Forests and Random Forest Regressors.}\label{fig:rr}
%\end{figure}

@@

 All the results of \fig{jur} and \fig{ant} show that in $\frac{10}{11}$ of our
 datasets, the baseline results are ranked significantly worse than the results seen
 after planning (evidence: the staistical ranking assigned by Scott-Knott is shown in the left-hand-side columns and most baselines get larger, i.e. worse, ranks
 that the treated data). The exception to this is SQL in  \fig{jur}. which
 seems to
 be resistant to our planning methods.

@@

%XXX begin rahul
One way to assess the validity of our predictions is to consider the space that generates
them. \fig{xxx} shows (1)~the training cases and (2)~the test cases and (3)~the
test cases displaced after applying HOW's plans for the {\em ant} data set.
In this figure, all the cases are projected onto two dimensions after (a)~creating one
data set with all of 1+2+3, finding their $x,y$ positions in the top-level {\tt cluster},
as generated by \fig{howcode}. Note that the both the test cases and the displaced test
cases all fall into nearly the same regions as the training data. This is to say that
predictors learned from the {\em ant} training data have some authority in the regions
used to generate our results\footnote{If the reader is concerned that this 2d projection
losses important information, then they should note that two separate  studies~\cite{papa13,divya15}
have confirmed that building defect predictors from this 2d space are just as effective
as predictors learned using all the defect attributes of \fig{ck}.}

\begin{figure}
\includegraphics
\end{figure}
%XXX end

@@

In summary, this paper makes five contributions:
\be
\item The HOW  case-based planner (which has not been presented before).
\item The experiments of this paper showing that HOW planner is useful for real-world tasks;
e.g. reducing the
expected values of the Jureczko software defects and the Seigmund software runtimes.
\item Apart from HOW, we  also offers a general framework for using  predictive system to build planners;
\item Further, we offer a  test to recognizes  when we should {\em not}  plan: specifically,
planning is
not recommended in domains with  poorly performing predictors;
\item Last, we  offer a general verification rig for assessing the value of plans generated within this rig.
\ee

@@

\bibliography{how}{}
\bibliographystyle{IEEEtran}
\end{document}

>>>>

\usepackage{subfig}
\usepackage{wrapfig}
 \usepackage{amsmath}
 \usepackage{url}
 \usepackage{pifont}
 %\usepackage{times}
\usepackage{rotating}
%\usepackage{balance} 
\usepackage{color, colortbl}
\usepackage{graphicx}
\usepackage{algorithmicx}
\usepackage[running]{lineno}
\usepackage{program}
\usepackage{cite}
\usepackage{alltt}
\usepackage{balance}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\textsection\ref{sec:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\definecolor{lightgray}{gray}{0.975}
\usepackage{fancyvrb}
\usepackage{stfloats}
\usepackage{multirow}
\usepackage{listings}
\usepackage{amsmath}  
\DeclareMathOperator*{\argmin}{arg\,min} 
\DeclareMathOperator*{\argmax}{arg\,max} 
%\usepackage[usenames]{xcolor}

@@

\title{Learning Actionable Analytics 
 (with applications for reducing defects and reducing runtimes)}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each Slope of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
Rahul Krishna, Tim Menzies, Xipeng Shen\\
        Computer Science, North Carolina State University, USA\\
       \{i.m.ralk, tim.menzies\}\@gmail.com, xshen5@ncsu.edu
 % use '\and' if you need 'another row' of author names
% 4th. author
\and
 Andrian Marcus\\
       Computer Science, UtDallas, USA \\
       amarcus@utdallas.edu }

@@

This is an open and pressing issue.
Business  users   now demand   data mining tools
that  support a  business-level
interpretation of that data. For example,
at a  panel on software analytics at ICSE'12,
industrial practitioners lamented the state of the art in data mining
and software engineering~\cite{menzies12a}. Panelists commented that
``prediction is all well and good, but what about decision
making?''. That is, these panelists are more interested in the interpretations
and follow-up
that occurs {\em after} the mining, rather than just  the mining itself; e.g.
\bi
\item 
Instead of just accepting  {\em predictions} on how many 
 software defects
to expect,  business users might now demand a {\em plan} to
reduce the likelihood of those defects;
\item Instead of just accepting {\em predictions} on the runtime
time of their software, business users might now demand
a {\em plan} to reduce that runtime.
\ei
How to assess such {\em plans}?
Some organizations have the resources to 
run repeated trials to assess  different treatments.
For example, in one remarkable recent study, Bente et al. report results
were the same specification was developed  by four different organizations~\cite{Anda2009}. Given those kind of resources, it would be possible
to (say) take a code base, assign it to $N$ different teams, apply
HOW's plans the code used by  $N/2$ teams, then check in 12 months time
if those halves of the teams have fewer defects than the other.

@@

The planner explored in this paper is the ``HOW'' case-based reasoner (CBR).
HOW's  ``plans'' are  set of changes
proposed  in order to better achieve some goal. 
Specifically, for every test case $Z$, HOW proposes a  plan $\delta$ to
  adjust   attributes $Z_j$:
\begin{equation}\label{eq:one}
Z_j = Z_j + \delta_j
\end{equation}
For example, to simplify a  large bug-prone  method, HOW might suggest
to a developer to reduce its size (i.e.  refactor that code by, say, splitting it across
two simpler functions).

@@

However, not all domains come with ready-to-use models. For example, 
consider software defect prediction and all the intricate issues that may lead defects in a product. A model that includes {\em all} those
potential issues would be very large and complex. Further,
the empirical data required to validate any/all parts
of that model can be hard to find.

In fact, our experience has been that accessing and/or commissioning
a model can be a labor-intensive process.
For  example, in previous work~\cite{me07f} we used models
developed by Boehm's group at the University of Southern California.
Those models inputted project descriptors to output predictors
of development effort, project risk, and defects.
Some of those models took decades to develop and mature (from 1981~\cite{boehm81} to 2000~\cite{boehm00b}).

@@

\subsection{Planning and AI}
HOW is a {\em probabilistic} planner, which is a different approach to that taken by
classical AI. 
That kind of planning is a logical procedure~\cite{Fikes1971}
that seeks an ordering on {\em operators} to take some domain
{\em state} from a {\em start} state to a {\em goal} state.
This classical logical approach is known to suffer from
computational bottlenecks~\cite{Bylander1994}. Hence,
like this paper,
many researchers take a probabilistic approach.
HOW's commitment to minimal displacement (and the fully-automated
modeling approach) of this paper makes it stand apart from, say,
  the Bayesian/Markov chain approach to planning of Dean et al.~\cite{dean1995planning}.

\subsection{Case-based Reasoning}
Case-based reasoning (CBR) has been extensively
explored in the AI literature
(where it has also bee called
 reasoning via analogy or instance-based reasoning).
CBR seeks to emulate human recollection and adaptation
of past experiences in order to find solutions to current
problems.

@@

Secondly, the output of a CBR is made on a ``case-by-case'' basis. 
That is, CBR does not offer some trite generalization over multiple
examples. Rather, the advice it gives is specialized to the particular
case being considered at the current time.  This is particularly attractive
since much of our recent work has focused on issues
of locality (where the best solutions for some part of the data
are very different some average case solution obtained from all the data~\cite{localvsglobal}).

@@

Generation two of that work resulted in  IDEA~\cite{me12c}.
IDEA and HOW use the    same recursive clustering
method but IDEA made the mistake of  summarizing those
recursive divisions into a tree structure. Initial results with IDEA were weak, but somewhat
positive~\cite{me12c}. We tried unsuccessfully for  months to extend and improve
the IDEA prototype. The results were most discouraging: those tree-based summaries often suffered
from the same optimization failure problem seen with W2.

@@

Turning now to the displacement {\em direction},
our experiments show that it is useful to  carefully reflect on exactly where HOW should  push each test case.
HOW replaces each cluster   with one {\em exemplar} that best
characterizes the data in that cluster. It then displaces the
test data towards that exemplar, as shown in \fig{howcode}, line 20. In summary, 
If  $Z_j$ is an independent variable within the
test case $Z$ and  $X$ is the exemplar found at training time,
then we displace $Z_j$ as follows:
\[Z_j =  Z_j + F*(X_j - Z_j)\]
Here, $F$ is the  magnitude controller, discussed above.

Different kinds of data require
different policies for exemplar generation.
For the Jureczko data, the objective score
is a Boolean which is  ``true'' if defects have been noted
for that class.  For this kind of data (with discrete objectives),
we found nothing better than  making the exemplar of a cluster be the mean
value of all attributes of all cases in that cluster.

However, for the Seigmund data, we found a better exemplar generation policy.
\fig{pp} shows the effects of selecting different kinds of exemplars for 
Berkeley DB, one of the Seigmund data sets.
The \textcolor{black}{\bf black baseline} curve  shows the runtimes for 600 random configurations
of the Makefiles used in Berkely DB. The other two curves shows the predictions of the runtimes if test cases are displaced towards exemplars
  built from:
\bi
\item The \textcolor{red}{\bf   mean}    value of all cases in the  cluster.
\item The  case with the \textcolor{green}{\bf  best}  objective score. 
\ei
Note that using the best as the exemplar does better than using the mean.
The general pattern shown of \fig{pp} has been seen in all the Seigmund data sets;
i.e. for data sets with continuous classes,
best results come from using exemplars formed from the best instance (and not the mean).

@@

    \caption{Training and test {\em data set properties} for the Jureczko data sets,
    sorted in ascending order of \% defective examples.
    On the right-hand-side, we show the {\em results from learning}.
    Data is ``good'' if it has   recalls over 60\% and false alarms under 40\%
(and note that, after tuning, there are more ``good'' than before).
Data   marked with ``$\star$'' show large improvements in performance, after tuning.
Data   marked with ``$\times$'' are not ``good'' since their test suites  have so few non-defective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
}\label{fig:j}
\end{figure*}

@@

As shown in \fig{work}, our proposal divides
project data  into two disjoint sets {\em train} and {\em test}
(so \mbox{{\em train} $\cap ${\em test} $=\;\emptyset$}).
Next, from the train set, we build both a {\em planner} as well
as a {  predictor}. Our general framework does not   commit to any particular  choice
of { planner} or { predictor} but, for the purposes of this paper, 
our { planner}
will be HOW  and our
our { predictors} will be the Random Forest~\cite{Breiman2001} and Random Forest
Regressor taken from the SciKit
Learn toolkit~\cite{Pedregosa2012}.  
%\begin{figure}[t!]
%\small
%\begin{tabular}{|p{.95\linewidth}|}\hline
% Decision tree learners find the attribute whose value's
%select for for sections of the data with least variation in the class
%variable. Decision tree learners then recurse on each selection~\cite{breiman84}. 
%
%A random forest is a set of decision trees, each built
%from some random subset of the rows and columns. The conclusions
%of the forest are a ``vote'' generated by all the trees~\cite{Breiman2001}. 
%
%A standard Random Forest predicts for a discrete class variable while
%a Random Forest Regressor generates numeric predictions.\\\hline
%\end{tabular}
%\caption{Random Forests and Random Forest Regressors.}\label{fig:rr}
%\end{figure}

@@

 The   results of \fig{jur} and \fig{ant} show that in $\frac{10}{11}$ of our
 data sets, the baseline results are ranked significantly worse than the results seen
 after planning (evidence: the statistical ranking assigned by Scott-Knott is shown in the left-hand-side columns and most baselines get larger, i.e. worse, ranks
 that the treated data). The exception to this is SQL in  \fig{jur}. which
 seems to
 be resistant to our planning methods.

@@

%XXX begin rahul
One way to assess the validity of our predictions is to consider the space that generates
them. \fig{howxy} shows (1)~the training cases and (2)~the test cases and (3)~the
test cases displaced after applying HOW's plans for the {\em ant} data set.
In this figure, all the cases are projected onto two dimensions by   finding their $x,y$ positions in the top-level {\tt cluster},
as generated by \fig{howcode}. Note that the  the   displaced test
cases   fall into nearly the same regions as the training data.

This pattern of \fig{howxy} (where the displaced test cases are found in the same
region as the training data) has been observed in all the other data sets studied in this
paper. Hence, the
predictors learned from thse training data have some authority in the regions
used to generate our predictions regarding the effects of planning\footnote{If the reader is concerned that this 2d projection
losses important information, then they should note that two separate  studies~\cite{papa13,divya15}
have confirmed that building defect predictors from this 2d space are just as effective
as predictors learned using all the defect attributes of \fig{ck}.}.

\begin{figure}
\begin{center}\includegraphics[width=3in]{figs/2d.png}\end{center}
\caption{Training cases (in gray), test cases (in red) and 
test cases displaced by HOW (in green). Note how the green and the gray occupy
the same regions; i.e. predictors trained on the training cases can be applied
to the displaced test cases.}\label{fig:howxy}
\end{figure}
%XXX end

@@

This paper has explored the problem of assess changes to a project without
extensive field studies. We have proposed using predictors learned from domain data
to serve as the oracle that judges the effectiveness of those changes.

The novel features of this paper are
\be
\item A general framework for using  predictive system to build planners (see \fig{work}).
For this paper, we used Random Forests as our predictor, but other predictors could
serve just as well.
\item A  test to recognizes  when we should {\em not}  plan: specifically,
planning is
not recommended in domains with  poorly performing predictors. In this paper, that
test excluded certain problematic defect data sets.
\item The HOW  case-based planner, which has not been presented before. HOW
is a significant improvement on our two prior implementations~\cite{6600685,me12c} that both
suffered
from {\em optimization failure}; i.e. when their recommendations were applied,
the resulting behavior actually got worse. We recommend HOW over that prior work
since none of our results exhibited such optimization failures.
\item The experiments of this paper, which showed that 
the HOW planner is useful for real-world tasks;
e.g. significantly reducing the
predicted values of the Jureczko software defects and the Seigmund software runtimes.
For those data sets, HOW
reduce
 the predicted values of defect counts and  runtimes to    
 72\%,75\%  (median) and 66\%,20\% (best case) of the initial values.
\ee 
As to when we would {\em not} use HOW, if  a domain has an accessible
and certified and well-maintained
domain model, then we would go beyond CBR and apply algorithms that can take
full advantage of the domain knowledge in those models; e.g. GALE, NSGA-II, NSGA-III, SPEA2, IBEA, particle swarm optimization, MOEA/D, etc.~\cite{krall14,deb00a,zit02,zit04,%
deb14,Cui2005a,zhang07:TEC}.

That said, one clear future direction would be explore
combinations of CBR tools with other approaches. 
One way to view HOW is a {\em local patch operator} that could be applied within 
GALE, NSGA*, etc (so in that combination, we would be trying to use   HOW's local patches to 
to optimize those optimizers).

@@

\bibliography{how}{}
\bibliographystyle{IEEEtran}
\balance
\end{document}
